Data for ms. 1

### 2017-04-05 ms1/ms1.Rmd
shouldnt lump amox/clav

  # keep only PDEs for known beneficiaries (semi join)
  # convert all amox/clav to just amox
  pde = read_tsv(sprintf('../pde_%i.tsv', this_year)) %>%
    semi_join(bene, by='bene_id') %>%
    mutate(antibiotic=if_else(antibiotic=='amoxicillin/clavulanate', 'amoxicillin', antibiotic))

>>>>

  # keep only PDEs for known beneficiaries (semi join)
  # convert all amox/clav to just amox
  pde = read_tsv(sprintf('../pde_%i.tsv', this_year)) %>%
    semi_join(bene, by='bene_id') #%>%
    #mutate(antibiotic=if_else(antibiotic=='amoxicillin/clavulanate', 'amoxicillin', antibiotic))
